\vskip-0.6in Trade Agreements in the Shadow of Lobbying\protect\footnote{Formerly circulated under the title ``Trade Agreements, Lobbying and Separation of Powers''}

### 2016-02-01 draft.tex
clean up sec:choices a bit, fix ref to pe_shocks, add transition after sec:pref

The home executive's welfare is specified as follows:
\[
  W_E = \mathit{CS}_X(\tau) + \ga_E \cdot \mathit{PS}_X(\tau) + \mathit{CS}_Y(\tau^*) + \mathit{PS}_Y(\tau^*) + \mathit{TR}(\tau)
\]
Note that this is identical to the welfare function for the legislature aside from the weight $\ga_E$ the executive places on the profits of the import industry, which is not a function of lobbying effort.

@@

In modeling the objective of the legislature, I introduce a variant of the general political support function introduced by Hillman (1982). While Hillman is credited with first proposing that policy makers choose tariffs in order to maximize their own political support, the PFS model contributed the explicit specification that lobbying contributions enter the political support function with constant marginal utility as $C + aW$.

@@

For the case of trade policy, ...

Notice that, aside from the endogeneity of the weight the legislature places on the lobbying industry's profits, this is precisely the \textit{deus ex machina} government objective function popularized by Baldwin (1987) that is commonly employed in the literature on the political economy of trade agreements. Since trade policies are overwhelmingly determined within the context of trade agreements, it is useful to have a framework to bring together the endogenous political pressure of PFS-style modeling with the trade agreements approach; the formulation in Equation~\ref{eq:ml} is intended as a bridge between the two. Buzard (2014a) for an example of how this form can be used to integrate the analysis of endogenous political activity and exogenous shocks to the political welfare of governments.

@@

\item Buzard, K., 2014a. Endogenous Politics and the Design of Trade Agreements. Available at: \url{https://kbuzard.expressions.syr.edu/wp-content/uploads/Endogenous-Politics.pdf}.

>>>>

The home executive's welfare is specified as follows:
\[
  W_E = \mathit{CS}_X(\tau) + \ga_E \cdot \mathit{PS}_X(\tau) + \mathit{CS}_Y(\tau^*) + \mathit{PS}_Y(\tau^*) + \mathit{TR}(\tau)
\]
Note that this is identical to the welfare function for the legislature aside from the weight $\ga_E$ the executive places on the profits of the import industry, which is not a function of lobbying effort. \textbf{Section~\ref{sec:choices} discusses these modeling choices in depth.}

@@

In modeling the objective of the legislature \textbf{(see Equation~\ref{eq:ml}), I have introduced} a variant of the general political support function introduced by Hillman (1982). While Hillman is credited with first proposing that policy makers choose tariffs in order to maximize their own political support, the PFS model contributed the explicit specification that lobbying contributions enter the political support function with constant marginal utility as $C + aW$.

@@

Notice that, aside from the endogeneity of the weight the legislature places on the lobbying industry's profits, this is precisely the \textit{deus ex machina} government objective function popularized by Baldwin (1987) that is commonly employed in the literature on the political economy of trade agreements. Since trade policies are overwhelmingly determined within the context of trade agreements, it is useful to have a framework to bring together the endogenous political pressure of PFS-style modeling with the trade agreements approach; the formulation in Equation~\ref{eq:ml} is intended as a bridge between the two. Buzard (2016) for an example of how this form can be used to integrate the analysis of endogenous political activity and exogenous shocks to the political welfare of governments.

@@

\item Buzard, K., 2016. Endogenous Politics and the Design of Trade Agreements. Available at: \url{https://kbuzard.expressions.syr.edu/wp-content/uploads/Endogenous-Politics.pdf}.
